Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
Update manuscript.Rmd

In total, 12 of 29 collared female caribou swam between islands in the Fogo
archipelago. Only 3 of these 12 had more than XX swimming events during the
study period, so approximately one third of our marked population swam
irregularly and infrequently, whereas for ~10% of individuals these swimming
events were relatively common, on average occurring once every 24 <!--confirm-->
days during ice-free seasons. We did not detect any swimming events for the
remaining 17 individuals; it remains unclear whether a subset of the population
does not engage in this behaviour at all, or whether these swimming events are
extremely rare for most caribou and we happened to detect some for those nine
individuals with very few observed swimming events. We are also unable to draw
conclusions about the prevalence of swimming in the ocean by male caribou: our
initial visual observation was of an adult male, but our GPS data only included
females.

>>>>

In total, 12 of 29 collared female caribou swam between islands in the Fogo
archipelago. Only 3 of these 12 had more than XX swimming events during the
study period; ~30% of the marked population swam at least XX times, whereas for
~10% of individuals these swimming events were relatively common, on average
occurring once every XX  days during ice-free seasons. We did not
detect any swimming events for the remaining 17 individuals. It remains unclear
whether these individuals do not swim, or whether swimming is rare for most caribou. 
We are also unable to draw conclusions about the prevalence of
swimming in the ocean by male caribou: our initial visual observation was of an
adult male, but our GPS data only included females.
